\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-09-11 paper.tex
Add detailed despcription and figure in Component - MAM

\subsection{Component}
\subsubsection{Masked Authenticated Messaging}
IOTA\cite{IOTAwhitepaper} is a feeless and scalable cryptocurrency for the IoT industry based on a the distributed  ledger consists of a directed acyclic graph(DAG) of individual transactions, \textbf{Tangle}. The innovative consensus algorithm allows people to make \textbf{zero-transactions} that one could store information securely within Tangle transactions. Nevertheless, publishing encrypted streaming data to distributed ledgers is still a challenge, which one need to keep the address and session key per message, otherwise attackers could easily issue spam transactions if publishing with the same address.

However, MAM resolves this problem, it is a second layer data communication protocol enables to emit and access an encrypted data stream over Tangle network and ensures data integrity.
It publishes each message to different addresses that each can be derived from the previous one, this forms a MAM channel. Furthermore, a session key can be provided to control the visibility and access to a MAM channel.

>>>>

\subsection{Components}
\subsubsection{Masked Authenticated Messaging}
IOTA\cite{IOTAwhitepaper} is a feeless and scalable cryptocurrency while MAM is the second layer data communication protocol built on top of Tangle.

MAM resolves the challenge to publish encrypted streaming data to distributed ledgers. It publishes messages encrypted with a \textbf{session key} to \textbf{channel}, which is a form of transactions that each address can be derived from the previous one. Therefore, with \textbf{channel root}, the first message of a channel, and the session key, all data on the channel is accessible.

One can create multiple channels as possible, however, the size of a channel is fixed which is decided before creation, thus data providers should decide how to distribute data product into MAM channels. While the creation of a MAM channel is time-consuming, brokers are also responsible for channel creation, encrypted data publishing and session key certification in our system. See Figure \ref{fig:launching_product}
